A Guide to Pre-Processing High-Throughput Animal Tracking Data

### 2021-02-04 docs/ms_atlas_preproc_main_text.tex
edit figure calibration  caption

% calibration figure
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.75\textwidth]{figures/fig_06_calib_residence_patch.png}
    \caption{Pre-processing steps for WATLAS calibration data showing filtering filtering on speed, median smoothing and thinning by aggregation, and making residence patches.
    \textbf{(a)} Positions with incoming and outgoing speed $\geq$ the 15 m/s are removed (N removed = 13,491, 26.6\%; grey crosses = removed, green points = retained).
    Rectangles show the region expanded in subfigures (b) and (c).
    \textbf{(b)} Expanded view of upper rectangle in (a) showing the raw data (grey crosses), the median smoothed positions (green circles; moving window $K$ = 5), and the smoothed track thinned by aggregation to a 30 second interval (purple squares).
    Square size corresponds to the number of positions used to calculate the averaged position during thinning, with no significant differences.
    Median smoothing retains all 37,324 observations (though changing their coordinates). Thinning aggregates these positions into 1,803 aggregates (4.8\% of the smoothed data volume).
    Median smoothing recovers a good estimate of the true track from significantly over-dispersed raw data, while thinning reduces the data volume but preserves track structure.
    \textbf{(c)} Classifying thinned data into residence patches yields robust estimates of the duration of known stops. The island of Griend (53.25$^{\circ}$N, 5.25$^{\circ}$E) is shown in beige.
    Residence patches (green polygons; function parameters in text) correspond well to the locations of known stops (purple crossed-squares).
    However, the algorithm identified all areas with prolonged residence, including those which were not intended stops, such as stops at the field station (n = 12; green polygon over red crossed-squares).
    The algorithm also failed to find two stops of 6 and 15 seconds duration, since these were lost in the data thinning step (crossed-square without green polygon shows one of these).}
    \label{fig:figure_calibration}
\end{figure}

>>>>

% calibration figure
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.75\textwidth]{figures/fig_06_calib_residence_patch.png}
    \caption{Pre-processing steps for WATLAS calibration data showing filtering filtering on speed, median smoothing and thinning by aggregation, and making residence patches.
    \textbf{(a)} Positions with incoming and outgoing speed $\geq$ 15 m/s are removed (grey crosses = removed, green points = retained).
    Rectangles show the region expanded in subfigures (b) and (c).
    \textbf{(b)} Expanded view of upper rectangle in (a) showing the raw data (grey crosses), the median smoothed positions (green circles; moving window $K$ = 5), and the smoothed track thinned by aggregation to a 30 second interval (purple squares).
    Square size corresponds to the number of positions used to calculate the averaged position during thinning, with no significant differences.
    While median smoothing retains all observations (though changing their coordinates), thinning aggregates these positions into approx. 5\% of the smoothed data volume.
    Median smoothing recovers a good estimate of the true track from significantly over-dispersed raw data, while thinning reduces the data volume but preserves track structure.
    \textbf{(c)} Classifying thinned data into residence patches yields robust estimates of the duration of known stops. The island of Griend (53.25$^{\circ}$N, 5.25$^{\circ}$E) is shown in beige.
    Residence patches (green polygons; function parameters in text) correspond well to the locations of known stops (purple crossed-squares).
    However, the algorithm identified all areas with prolonged residence, including those which were not intended stops, such as stops at the field station (n = 12; green polygon over red crossed-squares).
    The algorithm also failed to find two stops of 6 and 15 seconds duration, since these were lost in the data thinning step (crossed-square without green polygon shows one of these).}
    \label{fig:figure_calibration}
\end{figure}
